---
title: "NLP_Psychotherapy_Methodology_Functions"
author: "Yael Gutman"
date: "`r Sys.Date()`"
output: html_document
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Load libraries
```{r libraries}
library(dplyr)
library(tidyr)
library(text2vec)
library(tidyverse)
library(tidytext)
library(ggplot2)
library(tm)
library(stringr)
library(pdftools)
library(scales)
library(reshape2)
library(textstem)
library(wordcloud)
library(ggraph)
library(widyr)
library(igraph)
library(patchwork)
library(GGally)
library(reshape2)
library(knitr)
library(kableExtra)
library(textclean)
library(Matrix)
library(readr)
library(lexicon)
library(proxy)
library(patchwork)
library(mgcv)
```

################### NLP Psychotherapy Methodology Functions ####################

This is a basic instruction manual on how to apply the three-layered NLP methodology functions to analyze psychotherapy transcripts as illustrated in the Thesis: *Natural Language Processing (NLP) techniques as methodology for psychotherapy research*. Each function required for the application of the methodology is presented along with a brief description. The last section offers a demonstration of the use of each function on an example case.

This instruction manual is composed of the following sections:

A) Cleaning and pre-processing
B) Level one: word frequency and TF-IDF values
C) Level two: sentiment analysis
D) Level three: PMI values and dot product summary
E) Case example application


# A) CLEANING AND PRE-PROCESSING -----------------------------------------------
Before any procedures can be applied, the transcript must undergo pre-processing steps (tokenization, low frequency word removal, removal of stop words, and lemmatization).

*Cleaning*
In order for a file to be pre-processed, it needs to be cleaned and adapted to the required format (lowercase, no speaker labels, no special characters, no brackets or parenthesis, no additional white spaces). The following is an example of a cleaning function adapted to the sample transcript used in Chapter V. Example Case of the thesis.

For the Chapter V. Example case transcript, the cleaning function was adapted to carry out the following steps: 
    * Replacing the end of line character "\n" with a single white space
    * Removal of speaker labels
    * Replacing the curly apostrophe with a straight apostrophe (the contraction function only recognizes straight apostrophes) 
    * Replaces contractions with its full form
    * Removal of text in parenthesis/brackets
    * Removal of digits and any remaining punctuation
    * Transforming text into lowercase
    * Removal of any additional white spaces
    
```{r example cleaning function}
# CLEANING FUNCTION ------------------------------------------------------------
clean_func <- function(text){
  # collapse into single string
  text <- paste(text, collapse = "\n")
  remov <- gsub("\n", " ", text)
  remov <- remov %>%
  str_replace_all("’", "'") %>% 
    replace_contraction() %>%
    str_replace_all("\\b[A-Z]{1}[0-9]+\\b", "") %>% # remove single uppercase letter folllowed by number
    str_replace_all("\\([^\\)]*\\)|\\[[^\\]]*\\]", "") %>% # remove text in parenthesis or brackets
    str_replace_all("\\s+", " ") %>% # remove additional space
    str_replace_all("[0-9]", "") %>%
    as.character() %>%
    removePunctuation(ucp = TRUE) %>% # removes all punctuation including parenthesis
    tolower() %>%
    str_replace_all("  ", " ") # this eliminates any remaining unwanted white space
  
  return(remov)
}
```

*Pre-processing*
The functions below take the cleaned text string as input and process it into the appropriate format for subsequent steps. Often, case-specific stop words not included in the general stop word lexicon (e.g. 'mhmm','uhh 'yeah'), can become apparent after an initial exploratory analysis of the tokens. Based on this, one may choose to add a customized list of stop words as an argument. The frequency threshold is a parameter selected by the researcher, which may require further experimentation.

```{r pre-processing functions}
# Tokenization: convert string to tibble and create tokens
token_func <- function(processed_text){
  
  # convert string into tibble
  text_df <- tibble(text = processed_text)
  
  # convert to tokens
  text_tokens <- text_df %>%
    unnest_tokens(word, text)
  
  return(text_tokens)
}

# Stop words removal
stop_words_removal <- function(text_tokens, custom_stop_words){
  # adds custom stop-words to stop-word lexicon
  stop_words <- rbind(stop_words, data.frame( word = custom_stop_words, lexicon = "custom"))
  
  # removes words in stop-word lexicon
  nostop_text_tokens <- text_tokens %>%
    anti_join(stop_words, by = "word")
  
  return(nostop_text_tokens)
}

# Lemmatization: uses textstem, however, results are not optimal (e.g. feelings and feel are not given the same lemma)
lemmatization_func <- function(nostop_text_tokens){
  
  # uses hash_lemmas lexicon to lemmatize the tokens
  lemm_tokens <- nostop_text_tokens %>%
    mutate(word = lemmatize_strings(word, dictionary = lexicon::hash_lemmas))
  
  return(lemm_tokens)
}

# Rare words removal: empty function for now
rare_words_removal <- function(lemm_tokens, freq_threshold){
  
  # Add row number to preserve order
  lemm_tokens <- lemm_tokens %>%
    mutate(row_num = row_number())
  
  # count n words
  lemma_count <- lemm_tokens %>%
    count(word)
  
  # filter words with count less than threshold
  norare_text_tokens <- lemm_tokens %>%
    inner_join(lemma_count %>% filter(n > freq_threshold), by = "word") %>%
    arrange(row_num) %>%
    dplyr::select(-row_num, -n)
  
  return(norare_text_tokens)
}

# function to carry out pre-processing steps on cleaned text. specify stop words and low frequency word removal threshold
  # input: a single string 
  # output: processed tokens
preprocess_pipeline <- function(text, custom_stop_words, freq_threshold){
  text_tokens <- token_func(text)
  nostop_text_tokens <- stop_words_removal(text_tokens, custom_stop_words)
  lemm_tokens <- lemmatization_func(nostop_text_tokens)
  processed_tokens <- rare_words_removal(lemm_tokens, freq_threshold)
  return(processed_tokens)
}
```

**For multiple sessions**
The steps are recommended to be applied for multiple sessions of a single treatment.
For this, each session transcript must be saved as a separate item in a list of transcripts. The full client transcript list can then be processed with the following code:

```{r proc tokens mutliple sessions}
# function to process each session's raw transcript and output the processed tokens
  # input: raw transcript list
  # output: a list of processed tokens per session
proc_multiple_sess <- function(transcript_list, custom_stop_words, freq_threshold){
  
  client_proc_toks_list <- list()
  for(s in 1:length(transcript_list)){
    text <- transcript_list[s]
    clean_text <- clean_func(text)
    proc_toks <- preprocess_pipeline(clean_text, custom_stop_words, freq_threshold)
    client_proc_toks_list[[s]] <- proc_toks
  }
  
return(client_proc_toks_list)
}
```

# B) LEVEL ONE: WORD FREQUENCY AND TF-IDF VALUES -------------------------------

The list of processed tokens per session, obtained in the previous step, requires an additional adaptation for the first level word frequency analysis. The first function generates a dataframe with two columns: one containing each of the processed tokens, and the other the corresponding session number.

```{r processed toks df}
# function to transform the processed tokens list into a dataframe with session number
  # input: processed tokens list per session
  # output: data frame of tokens by session (for level one analysis)
proc_toks_df_func <- function(client_proc_toks_list){  
  # create a dataframe of tokens by session number
  sess_bind <- data_frame(word = c(), session = c())
  for(s in 1:length(client_proc_toks_list)){
    sess <- client_proc_toks_list[[s]]
    sess <- sess %>%
      mutate(session = paste0("Session_", s))
    sess_bind <- rbind(sess_bind, sess)
  }
proc_toks_df <- sess_bind
return(proc_toks_df)
}
```

The next function uses the obtained dataframe of processed tokens per session to calculate the tf-idf values, based on every unique word's distribution across the full treatment. The output of this function is a data frame with the tf-idf values displayed in descending order, where the highest tf-idf-valued word indicates a word with a high but specific frequency to that particular session.

```{r tf-idf function}
# function to calculate tf-idf values from processed tokens df
  # input: a dataframe containing a column of tokens and a column of the corresponding session number
  # output: dataframe of tf-idf values in descending order
tf_idf_func <- function(proc_toks_df){
  
  # count words per session df
  client_count <- proc_toks_df %>%
  count(session, word, sort = TRUE)
  
  # calculate total words per session
  total_words <- client_count %>%
    group_by(session) %>%
    summarize(total = sum(n))
  
  # calculate tf
  session_words <- left_join(client_count, total_words) %>%
    mutate(tf = n/total)

  # convert session to factor
  session_words$session <- as.factor(session_words$session)

  # calculate tf-idf and arrange in descending value
  session_words <- session_words %>%
    mutate(session_number = str_extract(session, "\\d+") %>% as.numeric())
    
  # calculate tf-idf   
  tfidf_words <- session_words %>%
    bind_tf_idf(word, session, n) %>%
    arrange(desc(tf_idf))
}
```

The function below generates bar plots of the top TF-IDF-valued n number of words for the specified session(s). The user must indicate the session numbers to be included, the amount of top n words, the tf-idf dataframe of values extracted from the previous step and the maximum value of the TF-IDF for adjusting the plot display.

*Visualization of TF-IDF values*
```{r function for tf-idf plots}
# function to generate the (highest) tf-idf values per session plot
  # input: tf-idf dataframe, session number and maximum value of tf-idf to adjust plot
  # output: a bar plot displaying the top 15 words of the session with highest tf-idf

tfidf_plots <- function(sess, top_n, tf_idf_df, max_y){
  # filter tf-idf dataframe for words in specificed session
  sess_tfidf <- tf_idf_df %>%
  filter(session_number %in% sess)

tfidf_plot <- sess_tfidf %>%
  # group tf-idf dataframe by session
  group_by(session) %>%
  arrange(desc(tf_idf)) %>%
  # select top n words
  slice_head(n = top_n) %>%
    ungroup() %>%
  mutate(word = reorder_within(word, tf_idf, session)) %>% 
  ggplot(aes(word, tf_idf, fill = session)) +
  ylim(0, max_y) +
  geom_col(show.legend = FALSE) +
  scale_x_reordered(name = NULL) +  
  labs(x = NULL, y = "tf-idf") +
  facet_wrap(~session_number, ncol = 3, scales = "free") +
  coord_flip() +
  ggtitle("Top 15 TF-IDF words for session") +
  theme(
    plot.title = element_text(hjust = 0.5, size = 11), # Center and bold title
    axis.title.x = element_text(size = 12),
    axis.title.y = element_text(size = 12)
  )

return(tfidf_plot)
}
```



# C) LEVEL TWO: SENTIMENT ANALYSIS ---------------------------------------------

*Sentiment-specific cleaning function*
In order to carry out the sentiment analysis, the original raw transcript needs to be formatted in a slightly modified version. Here the transcript is divided by numbered lines of text, which are then used for counting sections of the session to assign sentiment scores. The previous cleaning function removed end of line characters ('\n'). In this case, the text is split into lines by identifying these characters. The user is advised to verify if the cleaning function offered below returns the expected cleaned text format (by comparing it with the example case output text shown in the last section), otherwise the function may need to be adjusted so that the raw transcript can be appropriately split by lines or sentences.

```{r clean text func}
# function to split by \n or \n\n characters to add line numbers
  # input: raw transcript
  # output: a dataframe containing each cleaned line as a separate string per row in column one, and the corresponding line number in column 2
clean_text_sent_func <- function(text){
  cleanSent_client <- text %>%
    replace_contraction() %>%
    str_replace_all("\\b[A-Z]{1}[0-9]+\\b", "") %>% # remove single uppercase letter folllowed by number
    str_replace_all("\\([^\\)]*\\)|\\[[^\\]]*\\]", "") %>% # remove text in parenthesis or brackets
    str_replace_all("[0-9]", "") %>%
    removePunctuation(ucp = TRUE) %>% # removes all punctuation including parenthesis
    tolower() %>%
    # splits text by end of line characters
    str_split(pattern = "\n{1,2}") %>%
    unlist() %>%
    as_tibble() %>%
    # add line number
    mutate(line = row_number())
  return(cleanSent_client)
}
```

The following function takes as arguments: a set of negations, the text split by lines with the corresponding line number, the amount of lines to include in a section, and the list of stop words. The previous function produced a dataframe with each row corresponding to a cleaned version of each line of the original text, with its corresponding line number. The negations are a list of negating words (e.g. "no", "not", "never") to use for reverse-scoring negated bigrams. 

```{r negation correcting function}
# negation-correcting sentiment analysis function
neg_corrected_sent <- function(text, index_n, custom_stop_words, negations){
  
  # make into bigrams
  bigrams_text <- text %>%
    unnest_tokens(bigram, value, token = "ngrams", n = 2) 
    #mutate(line = text$line)
  
  # separate them
  bigram_sep <- bigrams_text %>%
    separate(bigram, c("word1", "word2"), sep = " ")
  
  # filter bigrams where word1 is a negation word
  negationb <- bigram_sep %>%
    filter(word1 %in% negations) %>%
    inner_join(get_sentiments(lexicon = "afinn"), by = c(word2 = "word")) %>%
    mutate(value = value * -1) %>% 
    unite(bigram, word1, word2, sep = " ") %>%
    mutate(word = bigram) %>%
    select(-bigram)
  
  # filter all rows with non-negation word 1 bigrams, make unique words again, then score sentiment
  unique <- bigram_sep %>%
    filter(!word1 %in% negations) %>%
    inner_join(get_sentiments(lexicon = "afinn"), by = c(word2 = "word")) %>%
    select(-word1) %>%
    filter(!word2 %in% stop_words$word) %>%
    filter(!word2 %in% negations) %>%
    mutate(word = word2) %>%
    select(-word2)
  
  # join back all words
  comb <- bind_rows(negationb, unique) %>%
    arrange(line)
  
  return(comb)
}
```

In order to process multiple sessions for one client, the list of transcript files is provided to the function below, which iterates over each item in the list and returns a list containing for each session a dataframe with three columns: the line number, sentiment value and the corresponding word.  

```{r sent scoring multiple sessions}
# function to apply sentiment scoring to multiple sessions
  # input: list of transcripts, negations, stop_words and section number
  # output: list of sentiment-scored sessions
sent_multiple_sess <- function(transcript_list, index_n, custom_stop_words){
    
  # cleaning transcripts for sentiment-specific format
    stop_words <- rbind(stop_words, data.frame(word = custom_stop_words, 
                                               lexicon = "custom"))
  
    negations <- c("no", "not", "never", "none", "neither", "nobody",
                   "nothing", "nowhere", "hardly", "scarcely", "barely",
                   "without", "except", "fail", "seldom")
    
    stop_words2 <- stop_words %>%
      filter(!word %in% negations)
  
  client_sent_list <- list()
  for(s in 1:length(transcript_list)){
    text <- transcript_list[[s]]
    clean_text <- clean_text_sent_func(text)
    sent_scored <- neg_corrected_sent(clean_text, index_n, custom_stop_words, negations) # negations, text, index_n, stop_words
    client_sent_list[[s]] <- sent_scored
  }
  
return(client_sent_list)
}
```

Once the sentiment scores have been generated per session, the following functions allow the user to generate visualizations (raw sentiment scores or GAM-smoothed sentiment signal). These visualizations can be generated in two main modalities: session-wise, where sentiment scores are displayed per sections of the session, or treatment-wise, where total sentiment scores are displayed by session number in the treatment.

```{r total sentiment summing functions}
# function to calculate sentiment total score per session
  # input: a dataframe of sentiment scores for one session
  # output: a sum of sentiment scores per specified section
sent_score_sess <- function(session_tokens, ind_n){
  
  # group lines by specified section parameter and sum total sentiment scores
  sent_scores <- session_tokens %>%
    group_by(index = line %/% ind_n) %>%
    summarise(sentiment = sum(value, na.rm = TRUE))
  return(sent_scores)
}

# function to calculate sentiment total score per complete treatment
  # input: a list of sentiment scores for multiple sessions
  # output: a vector of the summed sentiment scores for multiple sessions
total_sent_scores <- function(client_sent_score_list, ind_n){
  
  # loop to fill with total sentiment scores
  client_total_sent_scores <- list()
  total_sents_all <- c()

  for(s in 1:length(client_sent_score_list)){
    client_sess_toks <- as.data.frame(client_sent_score_list[s])
    client_sess_sent <- sent_score_sess(client_sess_toks, ind_n)
    client_total_sent_scores[[s]] <- client_sess_sent
    total_sents_all[s] <- sum(client_sess_sent$sentiment)
  }
  return(total_sents_all)
}
```

*Single session vs. full treatment sentiment analysis*
As mentioned above, sentiment plots can be generated in two main modalities: single or full-treatment. The functions below allow the user to select the modality. If 'single' the sentiment plots will be generated for the specified session number and section size, so that sentiment scores are summed for each section (e.g. 20 lines) and plotted for a single session transcript. In case the user selects full-treatment, the sentiment scores will be summed both per specified section size and also as a single summed sentiment per session, which is then plotted along the session number. The sentiment plot may be generated for raw sentiment scores or as a GAM-smoothed sentiment signal.

```{r single vs. full raw sentiment plots}
# single session raw sentiment plotting function
  # input: sentiment scores per session list session number, section number, and y-coordinate limits
  # output: a raw sentiment by section plot for a single session analysis
session_raw_sent <- function(client_sent_score_list, plot_modality, sess, ind_n){
  
  if(plot_modality == 'single'){
    # extract session number from sentiment score list
    sess_toks <- client_sent_score_list[[sess]]
    # classify as positive vs. negative
    sess_scored <- sent_score_sess(sess_toks, ind_n) %>%
      mutate(tot_sent = as.factor(ifelse(sentiment > 0, "positive", "negative")))
    
    # plot sentiment scores by section
    sess_plot <- ggplot(sess_scored, aes(index, sentiment)) +
    geom_point(aes(col = tot_sent), size = 2) + 
    geom_line(data = sess_scored, aes(index, sentiment), size = 0.5) +
    scale_color_manual(values = c("negative" = "red", "positive" = "green")) +
    theme_bw() +
    geom_vline(xintercept = 0, color = "black", size=0.3) +
    geom_hline(yintercept = 0, color = "black", size=0.3) +
    labs( title = paste0("Session raw sentiment scores per section ", sess),
          x = "Section",
          y = "Net sentiment score",
          color = "Total sentiment") +
    theme(plot.title = element_text(hjust = 0.5, face = "bold", size = 12))
    
    return(sess_plot)
  }
  
  else if(plot_modality == 'full'){
    nsess <- length(client_sent_score_list)
    
    # loop to fill with total sentiment scores
      client_total_sent_scores <- list()
      total_sents_all <- c()

    # assign total sentiment scores per session in full treatment
      total_sents_all <- total_sent_scores(client_sent_score_list, ind_n)
  
    # create dataframe to store total sentiment scores
    client_total_sent_df <- data.frame(session = c(1:nsess), 
                                      total_sent = total_sents_all)
    # classify score as either positive or negative
    client_total_sent_df <- client_total_sent_df %>%
      mutate(sentiment = as.factor(ifelse(total_sent > 0, "positive", "negative")))
  
    # plot sentiment scores by session number
    full_splot <- ggplot(client_total_sent_df, aes(session, total_sent)) +
      geom_point(aes(col = sentiment), size = 2) + 
      geom_line(data = client_total_sent_df, aes(session, total_sent), size = 0.5) +
      scale_color_manual(values = c("negative" = "red", "positive" = "green")) +
      theme_bw() +
      geom_vline(xintercept = 0, color = "black", size=0.3) +
      geom_hline(yintercept = 0, color = "black", size=0.3) +
      labs( title = "Full treatment raw sentiment scores",
            x = "Session",
            y = "Net sentiment score",
            color = "Total sentiment") +
      theme(plot.title = element_text(hjust = 0.5, face = "bold", size = 12))
    
    return(full_splot)
  }
  
  else{
    print("Error, please specify a valid plot modality")
  }
}
```

```{r single vs. full GAM sentiment analysis plot}
# gam-smoothed sentiment plotting function
  # input: sentiment scores per session list, plot modality (either single or full), the session number if plot modality is 'single', and the section size
  # output: a GAM-smoothed sentiment analysis plot
sent_gam_func <- function(client_sent_score_list, plot_modality, sess, ind_n){
  
  nsess <- length(client_sent_score_list)
  
  if(plot_modality == 'single'){
    # extract session number from sentiment score list
    sess_toks <- client_sent_score_list[[sess]]
    # classify as positive vs. negative
    sess_scored <- sent_score_sess(sess_toks, ind_n) %>%
      mutate(tot_sent = as.factor(ifelse(sentiment > 0, "positive", "negative")))
    
    # GAM plot
    sent_gam <- gam(sentiment ~ s(index), data = sess_scored)
    # create a sequence of index values for a smooth curve
    index_seq <- seq(min(sess_scored$index),
                   max(sess_scored$index),
                   length.out = 500)
    # create new data for prediction
    new_data <- data.frame(index = index_seq)
    # predict using the GAM model
    smoothed_preds <- predict(sent_gam, newdata = new_data)
    # plot of gam-smoothed line
    plot(index_seq, smoothed_preds, type = "l",
       xlab = "Section", ylab = "Net sentiment score",
       main = "")
    abline(h = 0, col = "black", lty = 2)
    title(paste0("GAM model-smoothed sentiment scores for session ", sess), font.main = 2)
  }
  
  else if(plot_modality == 'full'){
    # calculate total sentiment
    total_sents_all <- total_sent_scores(client_sent_score_list, ind_n)
  
    # create dataframe to store total sentiment scores
    client_total_sent_df <- data.frame(session = c(1:nsess), 
                                      total_sent = total_sents_all)
    
    # classify score as either positive or negative
    client_total_sent_df <- client_total_sent_df %>%
        mutate(sentiment = as.factor(ifelse(total_sent > 0, "positive", "negative")))
    
    # count number of sessions
    n_unique <- length(unique(client_total_sent_df$session))
    
    # if number of sessions below 5 return warning
      if (n_unique < 5) {
      stop(paste0(
        "Not enough data points to fit a GAM smoother (only ", n_unique, 
        " unique values)."
      ))
    }
    
    # if session number is low, the number of basis functions needs to be reduced 
    k_value <- if (n_unique >= 5 && n_unique < 10) 4 else NULL
    
    # if session number less than 10, readjust basis functions parameter
    if (!is.null(k_value)) {
      client_gam <- gam(total_sent ~ s(session, k = k_value), data = client_total_sent_df)
    } else {
      client_gam <- gam(total_sent ~ s(session), data = client_total_sent_df)  # use default k
    }
    
    # GAM plot
    df <- client_gam$model  
    pred <- predict(client_gam)
    
    # plot predicted values
    plot(df$session, pred, type = "l", 
         xlab = "Session", ylab = "Net sentiment score", 
         main = "")
    abline(h = 0, col = "black", lty = 2)
    title("Full-treatment GAM-smoothed sentiment signal", font.main = 2)
  }
  
  else{
    print("Error, please specify a valid plot modality")
  }
}
```


# D) LEVEL THREE: PMI VALUES AND DOT PRODUCT SUMMARY ---------------------------
*Co-occurrence matrix and PMI values*
In order to generate the co-occurrence matrix, which is then transformed into a PMI matrix per session, the functions below require the same processed tokens extracted from the pre-processing function in part A) CLEANING AND PRE-PROCESSING. 

First the individual functions need to be run:
```{r co-occurrence to PMI matrix functions}
### Functions: co-occ matrix, word_count, pmi_formula_COR, assoc_matrix_func_COR, pipeline_matrices_func_COR
# PMI matrix function correction --------------------------------------------
co_occ_matrix_func_COR <- function(lemm_tokens, window_size, weights){
  
  if(is.null(weights) == TRUE){
    weights <- rep(1, window_size)
  }
  else{
    weights <- 1/seq_len(window_size)
  }
  
  # create an iterator and a unique vocabulary of terms
  words_ls <- list(lemm_tokens$word)
  it <- itoken(words_ls, progressbar = FALSE ) # itoken: allows the iteration of each token at a time, for memory purposes
  vocab <- create_vocabulary(it) 
  
  # create a token co-occurrence matrix (TCM) using iterator, vectorizer and specified window
  vectorizer <- vocab_vectorizer(vocab) 
  tcm <- create_tcm(it, vectorizer, weights, skip_grams_window = window_size,
                    skip_grams_window_context = "symmetric")

  # symmetrize matrix
  tcm_matrix <- as.matrix(tcm)
  tcm_matrix[lower.tri(tcm_matrix)] <- t(tcm_matrix)[lower.tri(tcm_matrix)]
  
  return(tcm_matrix)
}

word_count <- function(final_tokens, tcm_matrix){
  # Create the dictionary with word counts
  word_counts <- final_tokens %>%
    group_by(word) %>%
    summarise(count = n(), .groups = 'drop')
  
  # arrange word counts in order of tcm
  tcm_words <- colnames(tcm_matrix)
  word_counts <- word_counts %>%
    mutate(word = factor(word, levels = tcm_words)) %>%
    arrange(word)
  word_counts <- word_counts$count
  
  return(word_counts)
}

pmi_formula_COR <- function(wco_prob, mult_ind_prob){
  value <- log2(wco_prob / mult_ind_prob)
  return(value)
}

assoc_matrix_func_COR <- function(tcm_matrix, tformula, n_words, word_counts){
  
  # convert into a sparse matrix
  tcm_sparse_matrix <-  Matrix(tcm_matrix, sparse=T)
  tcm_sparse_matrix <- as(tcm_sparse_matrix, "TsparseMatrix")
  
  # Calculate independent word-co-occurrence probabilities for each word
  row_prob <- word_counts / n_words
  col_prob <- word_counts / n_words
  
  # Create a sparse matrix to store PMI values
  r_words <- nrow(tcm_sparse_matrix)
  c_words <- ncol(tcm_sparse_matrix)
  tmatrix <- matrix(0, nrow = r_words, ncol = c_words)
  
  # Iterate over non-zero elements of the sparse matrix
  for (i in seq_len(length(tcm_sparse_matrix@x))){
    r <- tcm_sparse_matrix@i[i] + 1  # Row index (convert from 0-based to 1-based)
    c <- tcm_sparse_matrix@j[i] + 1  # Column index (convert from 0-based to 1-based)
    wco <- tcm_sparse_matrix@x[i]    # Word co-occurrence count
    
    # pair word co-occurrence probability
    wco_prob <- ( wco / n_words )
    
    # multiplied independent probabilities for each word
    mult_ind_prob <- ( row_prob[r] * col_prob[c] )
    if(mult_ind_prob == 0){
      tmatrix[r, c] <- 0
    }
    else{
      # calculate association measure according to given formula
      tmatrix[r, c] <- tformula(wco_prob, mult_ind_prob)
    }
  }
  # make matrix sparse and symmetrize
  tmatrix <- Matrix(tmatrix, sparse=T)
  pmi_matrix <- as.matrix(tmatrix)
  pmi_matrix[lower.tri(pmi_matrix)] <- t(pmi_matrix)[lower.tri(pmi_matrix)]
  return(pmi_matrix)
}
```

This function then generates the PMI matrix taking the processed tokens as input:
```{r generate PMI matrices}
# function to generate PMI matrix per session
  # input: list of processed tokens per session and specified arguments
  # output: list of PMI matrices per session 
PMI_func <- function(client_proc_toks_list, window_size, custom_stop_words, freq_threshold, weights){

  PMI_list <- list()
  
    for(s in 1:length(client_proc_toks_list)){
      # extract each session processed tokens
      s_proc_toks <- client_proc_toks_list[[s]]
      # get unique number of words per session
      n_words <- length(s_proc_toks$word)
    
      # Co-occurrence matrix + transformations: PMI, Chi^2, cosine similarity
      tcm_matrix <- co_occ_matrix_func_COR(s_proc_toks, window_size, weights)
      word_counts <- word_count(s_proc_toks, tcm_matrix)
      pmi_matrix <- as.matrix(assoc_matrix_func_COR(tcm_matrix, pmi_formula_COR, n_words, word_counts))
      
      # re-assign column and row names
      colnames(pmi_matrix) <- colnames(tcm_matrix)
      rownames(pmi_matrix) <- rownames(tcm_matrix)
      PMI_list[[s]] <- pmi_matrix
    }
  return(PMI_list)
}
```

Once the PMI matrices have been generated, the user may run the following functions, which calculates the dot products between all possible word pairs for each session, and generates a dot product summary dataframe (mean, variance, coefficient of variation).

*Dot product functions*
```{r dot product functions}
# dot product calculation without same word pairs
dot_prod_func_unique <- function(df){
  
# create matrix with # of rows = half of matrix and diagonal (since it is symmetrical)
  dot_matrix <- matrix(NA, nrow = (nrow(df)*(nrow(df) - 1))/2, ncol = 3)
  vocab <- colnames(df)
  rowN <- 1
  for(v in vocab){
    for (w in vocab){
      if( v != w) {
        # avoid repeated pairs
       if (which(vocab == v) < which(vocab == w)) {
          # first word in pair
          dot_matrix[rowN,1] <- v
          # second word in pair
          dot_matrix[rowN,2] <- w
        
          # calculate 'pure' dot product
          dp <- sum(df[,v] * df[,w])
          dot_matrix[rowN,3] <- dp
        
          # update row value
          rowN <- rowN + 1
       }
      }
    } 
  }
  dot_matrix <- na.omit(dot_matrix)
  colnames(dot_matrix) <- c("word1", "word2", "dp")
  dot_df <- as.data.frame(dot_matrix)
  dot_df[,3] <- as.numeric(dot_df[,3])
  return(dot_df)
}

mean_var_dp_func <- function(dot_df){
  mean_var_dp_df <- data_frame(mean_dp = mean(dot_df$dp), 
                               var_dp = var(dot_df$dp))
  return(mean_var_dp_df)
}

dp_all_sessions <- function(client_PMI_list){
  # dp calculation for all sessions
  dp_list <- list()
  vocab <- list()
  
  # from 1 to max sessions load files, apply dp function and save into list
  for(s in seq_along(client_PMI_list)){
    sess_pmi <- client_PMI_list[[s]]
    sess_names <- colnames(sess_pmi)
    
    # turn pmi into matrix
    pmi_matrix <- as.matrix(sess_pmi)
    sess_df <- sess_pmi
    rownames(sess_df) <- sess_names
    
    # get dp df
    sess_dp <- dot_prod_func_unique(sess_df)
    dp_list[[s]] <- sess_dp
    vocab[[s]] <- sess_names
  }
  return(list(dp_list = dp_list, vocab = vocab))
}

# function to create a df summarizing dot products for a session
dp_df_func <- function(client_dp_list, max_sess){
  client_dp_all <- client_dp_list$dp_list
  client_dp_vocab <- client_dp_list$vocab
  
  client_vals_df <- data.frame(session = c(1:max_sess), mean = NA, var = NA)
  for(s in 1:length(client_dp_all)){
    data <- client_dp_all[[s]]
    client_vals_df[s,2] <- mean(data$dp)
    client_vals_df[s,3] <- var(data$dp)
  }
  
  # adding a coefficient of variation column
  client_sd <- sqrt(client_vals_df$var)
  client_vals_df <- client_vals_df %>%
    mutate(var_coeff = client_sd/client_vals_df$mean)
  return(client_vals_df)
} 
```

The next function takes the PMI list, and returns a list with the dot products calculated per session, as well as a single dataframe with the dot product summary.

```{r generate dot products}
# function to generate dot products
  # input: PMI matrix per session list
  # output: dot product per session list and dot product full-treatment summary
dot_prod_function <- function(PMI_list){
  max_sess = length(PMI_list)
  
  dp_list <- dp_all_sessions(PMI_list)
  dp_summ <- dp_df_func(dp_list, max_sess)
  return(list(dp_list = dp_list, dp_summ = dp_summ))
}
```

A conceptual space plot can be generated for any dot product of interest. The function below provides the option to generate the conceptual space plot for the highest dot product word pair of a selected session. It accepts as arguments the full-treatment PMI matrix list, the dot product list, the session number and the limits for the y-coordinates.

*Conceptual space plots*
```{r highest dp function}
# function to extract highest dp and generate conceptual space plot
  # input: PMI list, dot product list, selected session for analysis and coordinate limits
  # output: conceptual space plot for the highest dot product of the session
high_dp_func <- function(PMI_list, dp_list, s_num, xylim){
  
  # extract dps for specified session and vocab list
  client_dps_s <- dp_list[[1]][[s_num]] %>%
  arrange(desc(dp))
  client_vocab_s <- dp_list[[2]][[s_num]]
  
  # extract word pair with highest dp 
  word1 <- client_dps_s[1,1]
  word2 <- client_dps_s[1,2]
  
  # PMI of specified session
  PMI_s <- as.data.frame(PMI_list[[s_num]])
  PMI_s$word <-  client_vocab_s
  
  # conceptual space plot
  client_conc_plot <- ggplot(PMI_s, aes(x = .data[[word1]], y = .data[[word2]])) +
    geom_point() +
    geom_hline(yintercept = 0, linetype = "solid", color = "black") +  # Add horizontal line at y = 0
    geom_vline(xintercept = 0, linetype = "solid", color = "black") +
    geom_abline(slope = 1, intercept = 0, linetype = "dotted", color = "black") +
    xlim(0,xylim) +
    ylim(-1.5,xylim) +
    xlab(word1) +
    ylab(word2) +
    ggtitle(paste0("Conceptual space plot for highest dot product of session ", s_num)) +
     theme_bw() +
    theme(plot.title = element_text(hjust = 0.5, size = 13)) +
      geom_text(aes(label = word), check_overlap = TRUE, size = 2.5, hjust = 0.5, vjust = -0.7) 
  
  return(client_conc_plot)
}
```

*Mean and variance plot*
```{r mean and variance plot}
# function to generate the mean vs. variance plot
  # input: dot product summary data frame extracted from the function 'dot_prod_function' and coordinate limits
  # output: a mean vs. variance plot for all of the sessions.
dp_mean_var_plot <- function(dp_summ, xlimm, ylimm){
  
  #calculate mean per means and variance
  mean_means <- mean(dp_summ$mean)
  mean_vars <- mean(dp_summ$var)
  
  # add line for session 1 variance 
  sess1_var <- dp_summ[1,3]
  
  # Added lines plot 1
  mean_var_plot <- ggplot(dp_summ, aes( x = mean, y = var, col = as.numeric(factor(session)))) +
    geom_point(size = 4) + 
    ggtitle("Dot product mean and variance per session") + 
    xlab("Mean") + 
    ylab("Variance") + 
    xlim(xlimm) +
    ylim(ylimm) +
    geom_hline(yintercept=sess1_var, linetype= "dashed", color = "darkgrey", size=0.5) +
    geom_vline(xintercept = mean_means, color = "blue", size=0.3) +
    geom_hline(yintercept = mean_vars, color = "blue", size=0.3) +
    #geom_abline(intercept = -11500, slope = 100, color = "black", size = 0.5) +
    scale_color_gradient(low = "lightgray", high = "purple") +
    theme_bw() +
    theme(plot.title = element_text(hjust = 0.5, face = "bold"),
          legend.position = "bottom") +
    labs(color = "Session number") +
      geom_text(aes(label = session), check_overlap = TRUE, size = 4, hjust = 1.2, vjust = -0.5) 
  
  return(mean_var_plot)
}
```

*Coefficient of variation plot*
```{r coeff of var plot}
# function for plotting the coefficient of variation per therapy session
  # input: dot product summary data frame
  # output: a full-treatment coefficient of variation plot by session number
dp_cv_plot <- function(dp_summ){
  
  cv_plot <- ggplot(dp_summ, aes(x = session, y = var_coeff)) +
      geom_line(aes(y = var_coeff), size = 0.7, col = "blue") +   
      labs(x = "Session", y = "CV", title = "Dot product coefficient of variation (CV)") +
      theme_minimal() + 
      theme(legend.title = element_blank()) +
      # adds the number of the session
      geom_text(aes(label = session), check_overlap = TRUE, size = 2.7, hjust = -0.3, vjust = -0.5) 
  
  return(cv_plot)
}
```


# E) CASE EXAMPLE APPLICATION -----------------------------------------------------
#####################   Example application   ######################

The use of the functions as they have been described in this tutorial are illustrated with the following example analysis, which makes use of the case transcripts presented in the book Counseling and Psychotherapy by Carl Rogers (1942). In this work, Carl introduces the complete phonographically recorded and transcribed case of Herbert Bryan, consisting of eight total sessions.

The session transcripts have been extracted from the book and saved separately as pdf files within the current folder, which can be read-in with the code presented below.

First we load the transcript files and then apply the pre-processing functions:
```{r read-in herbert session transcripts}
# read-in the transcript files and save into a list
herb_transcripts <- list()
for(s in c(1:8)){
  herb_sess <- pdf_text(paste0("Session ", s," - The Case of Herbert Bryan - Carl Rogers.pdf"))
  herb_transcripts[[s]] <- herb_sess
}

# apply pre-processing function to transcript list, 
  # specificy custom stop words and low-freq threshold
custom_stop_words <- c("mhm")
proc_toks_herb <- proc_multiple_sess(herb_transcripts, custom_stop_words = custom_stop_words, freq_threshold = 2)
```

# Level One 
Then we apply the tf-idf functions and plot the top 15 highest TF-IDF-valued words for session 1:

```{r inspect tf-idf vals}
proc_herb_df <- proc_toks_df_func(proc_toks_herb) 
herb_tfidf <- tf_idf_func(proc_herb_df)

# plot for session 1
tfidf_plots(sess = 1, top_n = 15, herb_tfidf, max_y = 0.10)
```

# Level Two
The following code applies the sentiment analysis functions and produces both a single session raw sentiment plot and a full-treatment (8 session) raw sentiment plot:

```{r sent analysis}
# apply sentiment analysis on raw Herbert transcripts with sections of 10 lines 
herb_sent_list <- sent_multiple_sess(herb_transcripts, index_n = 10, custom_stop_words)

# example use of raw sentiment scores function for a single session
session_raw_sent(herb_sent_list, plot_modality = 'single', sess = 1, ind_n = 5)

# example use of raw sentiment scores function for full-treatment
session_raw_sent(herb_sent_list, plot_modality = 'full', ind_n = 10)
```

Below, the GAM signal has been extracted for both the single session and full-treatment sentiment analysis. Important to note here is that if the session number is too low (below 10), it becomes more difficult to apply a GAM model on the data, since it requires enough information (multiple unique values) to accurately estimate the smoothing functions. The function applied here determines if the amount of sessions is below the threshold of 10, for which the parameter of basis functions is adjusted to a lower value. With too few sessions it would be advised to fit a simpler function instead (e.g. linear regression).

```{r example for running GAM-smoothed sentiment plot}
sent_gam_func(herb_sent_list, plot_modality = 'single', sess = 1, ind_n = 10)
sent_gam_func(herb_sent_list, plot_modality = 'full', ind_n = 10)
```

# Level Three
The following code takes as input the pre-processed tokens, obtained from an earlier step to generate the PMI list, as well as the dot product list and summary data frame.

Some parameters need to be specified before applying the function such as weights and the frequency threshold. The weights have been set to null, which means all words counted within the sliding window of proximity to neighboring words receive an equal weight when calculating total co-occurrence values. However, the weights could be modified, for example, to increase in value by proximity to the target word (so that the co-occurrence value is increased for words that appear closer to the target word).

```{r PMI and dot product values}
# parameter setting
weights <- NULL
freq_thresh <- 2

# applying PMI, and dot product generating functions
herb_PMI_list <- PMI_func(proc_toks_herb, window_size = 5, custom_stop_words, freq_threshold = 2, weights = weights)
herb_dp <- dot_prod_function(herb_PMI_list)
herb_dp_list <- herb_dp$dp_list
herb_dp_summ <- herb_dp$dp_summ
```

Having obtained the PMI and dot product values per session, the following code presents a series of visualizations to examine the values:

  * The first two plots show the conceptual space plots for the highest dot product word pair for sessions 1 and 2.
  * The third plot displays the mean and variance dot products across all eight sessions.
  * The fourth plot shows the coefficient of variation obtained across sessions, offering a chronological display of the dot product statistical summary measure through the treatment trajectory.
  
The user may need to examine the range of values to set the right coordinate limits. Here the limits for the mean and variance plot were obtained from the dot product summary dataframe, extracted in the previous step.

```{r plots}
high_dp_func(herb_PMI_list, herb_dp_list, s_num = 1, xylim = 6)
# to set the correct coordinate limits inspect the range of the dot product mean and variance values
high_dp_func(herb_PMI_list, herb_dp_list, s_num = 2, xylim = 6)
# to set the correct coordinate limits inspect the range of the dot product mean and variance values
range(herb_dp_summ$mean)
range(herb_dp_summ$var)
dp_mean_var_plot(herb_dp_summ, c(100,200), c(5000,15000))
dp_cv_plot(herb_dp_summ)
```

This tutorial presented a brief example of some of the visualizations that may be extracted with the use of these functions. The user may explore with more detail the differences in values across multiple sessions and in multiple visualizations. They may also wish to consult back to the original raw qualitative transcript to obtain a richer qualitative understanding of the case, as this may be necessary to provide the qualitative context in which to situate the extracted language feature values as observed above.

###################   Reference   ####################
Rogers, C. R. (1942). Counseling and Psychotherapy: Newer concepts in practice. Houghton Mifflin






